An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps

### 2020-01-16 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
parameter tables not used

```{r setup, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE}
library(knitcitations)
library(RefManageR)
library(sf)

@@

The following must be provided to \code{create_hexmap}:
```{r table_necessary, echo = FALSE, fig.cap = "This table details the parameters that must be provided to create a hexagon tile map using sugarbag."}
library(sugarbag)
library(tidyverse)

knitr::kable(tibble::tibble(parameter = c('shp', 
  'sf_id',
  'focal_points'),
  description = c(
    'an sf object containing the polygon information', 
    'name of a column that distinguishes unique areas',
    'a data frame of reference locations used to allocate hexagons'
    )), format = "latex")
```

@@

```{r parameters, echo = FALSE, fig.cap = "This table details the additional parameters that are used to create a hexagon tile map using sugarbag."}
knitr::kable(tibble(parameter = c('buffer_dist', 'hex_size',  'hex_filter', 'width'),
  description = c('a float value for distance in degrees to extend beyond the geometry provided',
    'a float value in degrees for the diameter of the hexagons', 'amount of hexagons around centroid to consider for allocation',
    'the angle used to filter the grid points around a centroid')), format = "latex")
```

@@

```{r centroids_plot, out.width = "100%", echo = FALSE, eval = FALSE, fig.cap="The geographic shapes of the Statistical Areas of Tasmania at Level 2. The points show the locations of the centroids of the SA2 areas."}
knitr::include_graphics(path = "figures/1centroids.png")
```

@@

```{r grid2, fig.cap="Grid points to create a tilegram.", out.width = "100%", echo = FALSE}
knitr::include_graphics(path = "figures/2grid.png")
```

@@

```{r buffers, echo = FALSE, out.width = "100%"}
knitr::include_graphics(path = "figures/4grid.png")
```

@@

```{r buffs, out.width = "100%", echo = FALSE}
knitr::include_graphics(path = "figures/6allocate.png")
```

@@

```{r eval=FALSE}
library(sugarbag)
```

>>>>

```{r setup, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE}
library(knitcitations)
library(RefManageR)
library(sf)
library(sugarbag)

@@

The following parameters must be provided to \code{create_hexmap}:

 - *shp:* an sf object containing the polygon information
 - *sf_id:* name of a column that distinguishes unique areas
 - *focal_points:* a data frame of reference locations used to allocate hexagons

@@

 - *buffer_dist:* a float value for distance in degrees to extend beyond the geometry provided
 - *hex_size:* a float value in degrees for the diameter of the hexagons
 - *hex_filter:* amount of hexagons around centroid to consider for allocation
 - *width:* the angle used to filter the grid points around a centroid

@@

```{r centroids_plot, out.width = "100%", echo = FALSE, eval = FALSE, fig.cap = "The geographic shapes of the Statistical Areas of Tasmania at Level 2. The points show the locations of the centroids of the SA2 areas."}
knitr::include_graphics(path = "figures/1centroids.png")
```

@@

```{r grid2, fig.cap = "Grid points to create a tilegram.", out.width = "100%", echo = FALSE}
knitr::include_graphics(path = "figures/2grid.png")
```

@@

```{r buffers, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "100%"}
knitr::include_graphics(path = "figures/4grid.png")
```

@@

```{r buffs, fig.cap = "A complete hexagon tile map of Tasmania.", out.width = "100%", echo = FALSE}
knitr::include_graphics(path = "figures/6allocate.png")
```

@@

```{r}
library(sugarbag)
```

### 2020-01-16 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
parameter tables not used

The following must be provided to \code{create_hexmap}:

\begin{tabular}{l|l}
\hline
parameter & description\\
\hline
shp & an sf object containing the polygon information\\
\hline
sf\_id & name of a column that distinguishes unique areas\\
\hline
focal\_points & a data frame of reference locations used to allocate hexagons\\
\hline
\end{tabular}

\end{CodeChunk}

@@

\begin{tabular}{l|l}
\hline
parameter & description\\
\hline
buffer\_dist & a float value for distance in degrees to extend beyond the geometry provided\\
\hline
hex\_size & a float value in degrees for the diameter of the hexagons\\
\hline
hex\_filter & amount of hexagons around centroid to consider for allocation\\
\hline
width & the angle used to filter the grid points around a centroid\\
\hline
\end{tabular}

\end{CodeChunk}

@@

\begin{center}\includegraphics[width=1\linewidth]{figures/4grid} \end{center}

\end{CodeChunk}

@@

\begin{center}\includegraphics[width=1\linewidth]{figures/6allocate} \end{center}

\end{CodeChunk}

>>>>

The following parameters must be provided to \code{create_hexmap}:

\begin{itemize}
\tightlist
\item
  \emph{shp:} an sf object containing the polygon information
\item
  \emph{sf\_id:} name of a column that distinguishes unique areas
\item
  \emph{focal\_points:} a data frame of reference locations used to
  allocate hexagons
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \emph{buffer\_dist:} a float value for distance in degrees to extend
  beyond the geometry provided
\item
  \emph{hex\_size:} a float value in degrees for the diameter of the
  hexagons
\item
  \emph{hex\_filter:} amount of hexagons around centroid to consider for
  allocation
\item
  \emph{width:} the angle used to filter the grid points around a
  centroid
\end{itemize}

@@

{\centering \includegraphics[width=1\linewidth]{figures/4grid}

\caption[Filter for grid points within a square, then circular, distance for those closest to the centroid]{Filter for grid points within a square, then circular, distance for those closest to the centroid.}\label{fig:buffers}
\end{figure}
\end{CodeChunk}

@@

{\centering \includegraphics[width=1\linewidth]{figures/6allocate}

\caption[A complete hexagon tile map of Tasmania]{A complete hexagon tile map of Tasmania.}\label{fig:buffs}
\end{figure}
\end{CodeChunk}
